---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# muscadet

<!-- badges: start -->
[![check-standard](https://github.com/LMJL-Alea/muscadet/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/LMJL-Alea/muscadet/actions/workflows/check-standard.yaml)
<!-- badges: end -->

The goal of **muscadet** is to provide a set of functions for simulating and estimating planar point patterns according to various two-mark DPP models. It currently provides support for Gaussian and Bessel DPPs.

## Installation

You can install the development version of muscadet from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LMJL-Alea/muscadet")
```

## Example

You can simulate a planar point pattern following a two-mark DPP using the
`rbidpp()` function:

```{r sim}
library(muscadet)
withr::with_seed(1234, {
  progressr::with_progress({
    df <- rbidpp(
      n = 1, 
      rho1 = 100, rho2 = 100, 
      alpha1 = 0.03, alpha2 = 0.03, 
      alpha12 = 0.035, tau = 0.5, 
      L = 1, model = "Gauss"
    )  
  })
})
```

You can estimate the parameters of a two-mark DPP from an observed planar point
pattern using the `estimate()` function:

```{r est}
estimate(df[[1]], model = "Gauss")
```
